R Notebook

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.14.22
so much fuckery

plotting
plot(dr_smug_ntWrk)
plot(tst_ntwrk)

from Rmd yeilds same error message

plotting from rScript is fine >.<

# it's a bloody statnet edgelist

View(indx_SmugglerCove_recip)
summary(indx_SmugglerCove_recip)

@@

                    #2nd passIt
passIt$substring_first <-     
  str_extract(
    passIt$X5,
    "(\\w+)")

#####

@@

                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3)
                       )
#####

@@

names(smugCovIdx )[1] <- "dnkName"
names(smugCovIdx )[2] <- "dnkIng"
names(smugCovIdx )[3] <- "dnkCode"   
names(smugCovIdx )[4] <- "classIng"

@@

# Network: Creating network Data

## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()

>>>>

# View(indx_SmugglerCove_recip)
summary(indx_SmugglerCove_recip)

@@

colnames(passIt)
                    #2nd passIt
passIt$substring_first <- 
  str_extract(passIt$X5,"(\\w+)")

colnames(passIt)
#####

@@

                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3,4)
                       )
colnames(passIt)
#####

@@

names(smugCovIdx )[1] <- "dnkName"
names(smugCovIdx )[2] <- "dnkIng"
names(smugCovIdx )[3] <- "ingType"

colnames(smugCovIdx)
```

# Network: Creating network Data
```{r NETWORK: Network Formation}
passIt <- smugCovIdx
dim(passIt)
  #####
        #### Edgelist: Network Formation
            ## NOTE: Edgelist Format
#####
            ## network data is nx2 (or more with edge attributes)
            ## first column is "From", 
            ## second column is "To"
  #####
          ### Edgelist: inspect column names
              ## inspect column names as 3rd-kth columns of network_data may include network attributes

colnames(passIt)

@@

```{r EDGELIST: IGRAPH: create a network object from the dataset, echo=TRUE}

 smug_unrIg <- smugCovIdx

smug_unrIg <-
  graph.data.frame(
    smug_unrIg[,1:3],
    directed = F)

summary(smug_unrIg)

##### Summary Output
#####
      # IGRAPH c6de075 UN-- 274 672 -- 
      # + attr: name (v/c), ingType (e/c)

```{r Edgelist: Statnet Network Object}

#Lets read the data into the enviroment.
#This will import it formatted as an edgelist

source_netEdge <- smugCovIdx

# Identify Edge Vertices and Edge Attributes

colnames(source_netEdge)
# dnkName <- "dnkName" 
# dnkIng <- "dnkIng"  
# edgeAT <- "ingType"

#Lets create an statnet object from our edgelist
#First we make the object. It will have no vertex or edge attributes
sourceEL_sn <- 
  network(as.matrix(source_netEdge[1:2], 
                    matrix.type = 'edgelist')
  )

#**%e%** Let's add edge atributes, do not include the colNames for edge vertex

sourceEL_sn%e%"ingType" <- source_netEdge$ingType
sourceEL_sn%e%"dnkIng" <- source_netEdge$dnkIng

# Generating the EdgeList

##**round 1**
          # from "_netEdge" select "colNames" to be identified with "vertex.names"

temp <- source_netEdge[,c("dnkName")]

##**round 2**
            # code still selecting from "_netEdge", add "colNames"

colnames(temp)<- c("dnkIng")

##**round 3**
            # "rBind" selects "colnames" from "_netEdge" and BINDS them to temp

temp<- rbind(temp, source_netEdge[, c("dnkIng")])

##**final round** !!! is being used as variable in generating an edgelist object
                # temp contains

sourceEL_sn%v%"dnkName"<- 
  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
                    temp$dnkIng)]

print(sourceEL_sn)

# it's a bloody statnet edgelist 
```

# Network Info
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()
